\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}
\usepackage{parskip}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{Intermediate Test 2 Solutions}
  \\ \vspace{1em}
  \textbf{\large Stellenbosch Camp 2022}
\end{center}

\bigskip

\begin{enumerate}[itemsep=24pt]

\item % Source of problem
Given positive real numbers $a$, $b$, and $c$ such that $a^2+b^2+c^2 = 26$ and $ab+bc+ca = 19$, find the value of $a+b+c$.

\textbf{Solution:} 
\[(a+b+c)^2 = (a^2+b^2+c^2) + 2(ab + bc + ca) = 26 + 2\cdot 19 = 8^2\]
\[\implies a+b+c = 8.\]

\item
Find all positive integers $a$ and $b$ such that 
$$a! + b! = 3^n -1 $$
where $n$ is a positive integer.

\textbf{Solution:} 
W.L.O.G. let $a\geq b$.

Case $1$: $a,b\geq3$\\
Note that $3|a!$ and $3|b!$, meaning $3|a!+b!$, but $3$ does not divide the RHS. Therefor there are no solutions for this case.

Case $2$: $b=1$
\begin{align*}
    a!+1&=3^n-1\\
    \implies \hspace{10mm} a!&=3^n-2 \hspace{15mm}
\end{align*}
if $a\geq3$ there are no solutions as $3$ will divide the RHS but not the LHS. Checking $a<3$ gives the solution $a=1, b=1, n=1$.

Case $3$: $a\geq3, b=2$
\begin{align*}
    a!+2&=3^n-1\\
    \implies \hspace{10mm} a!&=3^n-3 \hspace{10mm} \\
    \implies \hspace{10mm} a!&=3(3^{n-1}-1) \hspace{7mm}
\end{align*}
if $a\geq6$ there are no solutions as $9$ will divide the RHS but not the LHS. Checking $a<6$ gives the solutions: $a=3, b=2, n=2$ and $a=4, b=2, n=3$

\item % Tsimerman
Show that if every room in a house has an even number of doors, then the number of outside entrance doors must be even as well.

\textbf{Solution:} Let $a_0, a_1, \dots, a_n$ be the number of doors you can see in room $i$ with $a_0$ being the number of outside doors. Notice that every door is counted twice so that $\sum_{i=0}^{n}a_i \equiv 0 \pmod 2$. Now since each door has an even number of rooms, we have $\sum_{i=1}^{n}a_i \equiv 0 \pmod 2$ so that $a_0 \equiv 0 \pmod 2$ as required. 


\item 
For acute triangle $\triangle ABC$, a point $Z$ interior to $\triangle ABC$ satisfies $ZB = ZC$.
Suppose points $X$ and $Y$ lie outside $\triangle ABC$ such that $\triangle XAB \mathop{|||} \triangle YCA \mathop{|||} \triangle ZBC$.
Prove that $A,X,Y,Z$ are the vertices of a parallelogram. 

\textbf{Solution:}
$$\angle ZCY = \angle ZCA + \angle ACY = \angle ZCA + \angle BCZ = \angle BCA$$
$$\frac{ZC}{BC} = \frac{YC}{AC} \qquad (\triangle ZCB \mathop{|||} \triangle YCA).$$
Therefore $\triangle BCA \mathop{|||} \triangle ZCY$ as the sides are in proportion and they share a common angle. Similarly $\triangle BCA \mathop{|||} \triangle BZX$. 

Since $BZ = ZC \implies \triangle BZX \equiv \triangle ZCY \implies XZ = YC = AY$ and $ZY = BX = XA$.
Therefore $AXZY$ is a parallelogram.


\item
For nonzero real numbers $a$, $b$, and $c$, show that
\[ \frac{a}{b} +\frac{b}{c} +\frac{c}{a} = \frac{a}{c} +\frac{c}{b} +\frac{b}{a} \]
if and only if two of $a$, $b$, and $c$ are equal.

\textbf{Solution:} Observe the following computation:
\begin{align*}
\frac{a^{2}b + b^{2}c + c^{2}a}{abc} & = \frac{a^{2}c + b^{2}a + c^{2}b}{abc}\\
 \iff 0 & = \frac{a^{2}c + b^{2}a + c^{2}b -(a^{2}b + b^{2}c + c^{2}a)}{abc} \\
 \iff 0 & = \frac{abc + a^{2}c + b^{2}a + c^{2}b - (a^{2}b + b^{2}c + c^{2}a+abc)}{abc} \\
 \iff 0 & = \frac{(a-b)(b-c)(c-a)}{abc} \\
\end{align*}
Thus one of $a-b$, $b-c$, $c-a$ must be zero, showing that some pair among $a$, $b$, $c$ must be equal.

\end{enumerate}

\end{document}
