\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Advanced Test 4}
  % LEVEL is Senior, Intermediate or Beginner
  % NUMBER is the test number: 1, 2, etc.
  \\ \vspace{1em}
  \textbf{\large Stellenbosch Camp 2022}
  \\ \vspace{1em}
  \textbf{\large Time: $2\frac{1}{2}$ hours}
\end{center}

\bigskip

\begin{enumerate}[itemsep=\fill]

\item % Emile, 2022
You have an $n\times n$ chessboard which starts with all its squares white. An operation involves choosing a row or column and flipping the colour of every square in this row or column between white and black. Is it possible that for all $0\leq k\leq n^2$, you can do some sequence of operations and end up with $k$ black squares?


\item %
Show that $2022 \times 2^n$ can be written as the sum of three distinct non-zero squares for every natural number $n$.


\item % Andrew McGregor, 2022.
A triple of positive real numbers $(a,b,c)$ is called \textit{good} if $a,b,c$ are the side lengths of a non-degenerate triangle, and \textit{cute} if $a,b,c$ are the sides of an acute angled triangle. Prove that $(a,b,c)$ is \textit{good} if and only if $(\sqrt{a},\sqrt{b},\sqrt{c})$ is \textit{cute}. 


\item % Baltic Way 1994
The incircle of $\triangle ABC$ is tangent to $BC,CA,$ and $AB$ at $D,E,$ and $F$ respectively. $P,Q,$ and $R$ are the incenter's of $\triangle AEF, \triangle BFD,$ and $\triangle CDE$ respectively. Prove that $DP, EQ, $and $RS$ are concurrent.


\item % Tsimelman, 2022
Every point in space is coloured red, blue, or green. Prove that for at least one of the 3 colours, the set of distances between points of that colour contains all positive real numbers.


\end{enumerate}


\vfill
% ASCII art
\centering
\scriptsize
\begin{BVerbatim}
                  _         _
 .-""-.          ( )-"```"-( )          .-""-.
/ O O  \          /         \          /  O O \
|O .-.  \        /   0 _ 0   \        /  .-. O|
\ (   )  '.    _|     (_)     |     .'  (   ) /
 '.`-'     '-./ |             |`\.-'     '-'.'
   \         |  \   \     /   /  |         /
    \        \   '.  '._.'  .'   /        /
     \        '.   `'-----'`   .'        /
      \   .'    '-._        .-'\   '.   /
       |/`          `'''''')    )    `\|
       /                  (    (      ,\
      ;                    \    '-..-'/ ;
      |                     '.       /  |
      |                       `'---'`   |
      ;                                 ;
       \                               /
        `.                           .'
          '-._                   _.-'
           __/`"  '  - - -  ' "`` \__
         /`            /^\           `\
         \(          .'   '.         )/
          '.(__(__.-'       '.__)__).'
\end{BVerbatim}

\end{document}
