\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large Intermediate Test 5}
  \\ \vspace{1em}
  \textbf{\large Stellenbosch Camp 2022}
  \\ \vspace{1em}
  \textbf{\large Time: $4$ hours}
\end{center}

\bigskip

\begin{enumerate}[itemsep=\fill]

\item % Tsimelman
Two baseball teams are playing each other in a best of 7 match, with each game having a definite winner (no draws). The teams are equally matched so that each game has an equal probability of either team winning. Another game will not be played once any team has won 4 out of the 7 games. Prove that the probability that the game will end in 6 games is the same as the probability that the game will end in 7 games.

 
\item % The Internet
Let $n$ be a positive integer. There are $n$ points in the plane such that any three of them form a triangle of area $1$. Prove that all the points lie inside a triangle of area $4$. 


\item % Kgaugelo
Let $x$, $y$ and $z$ be positive real numbers. Show that 
$$ (x+y+z)\left(\frac{1}{x}+\frac{1}{y}+\frac{1}{z}\right) \geq 9. $$

\vspace{-12pt}


\item % Finland, 2016
The center of the circumcircle of the acute triangle $ABC$ is $O$, and the circumcircle of $ABO$ meets $BC$ and $AC$ at $P$ and $Q$ ($P\neq B$).
Show that the extension of the line $CO$ is perpendicular to $PQ$.


\item % Parvardi, Functional Equations Problems
Find all functions $f : \mathbb{R} \to \mathbb{R}$ such that \[ f(x+y) = f(x^2+y^2) \] for all $x,y \in \mathbb{R}$.


\item % Tsimelman
The game of Chomp is played on an $n \times n$ board by Dylan (on behalf of SA) and Fionn (on behalf of Ireland) as follows: Dylan moves first.
On a player's move, they must place an X on any square $(i, j)$ which does not yet have an X on it, and they must also fill in an X on any square above and to the right of that square which does not yet have an X on it.
That is, any square $(s, t)$ with $s \geq i$ and $t \geq j$ which does not yet have an X also gets an X filled in.
The person who places the last X loses.
Is there a winning strategy for either player?

\end{enumerate}


\vfill
% ASCII art
\centering
\small
\begin{BVerbatim}
 __         __
/  \.-"""-./  \
\    -   -    /
 |   o   o   |
 \  .-'''-.  /
  '-\__Y__/-'
     `---`
\end{BVerbatim}

\end{document}
