\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\newcommand*{\floor}[1]{\left\lfloor#1\right\rfloor}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large February Advanced Monthly Problem Set}
  \\ \vspace{1em}
  \textbf{\large Due: 13 March 2023}
\end{center}

\bigskip

\begin{enumerate}[itemsep=\fill]

\item % DB-2017-1
Let $ABC$ be a triangle with circumcentre $O$ and circumradius $R$ such that $\angle A = 45^\circ$.
Let $BO$ (extended) meet $AC$ at $E$ and let $CO$ (extended) meet $AB$ at $F$.
Find $BE \cdot CF$ in terms of $R$.

 
\item % Tim
Let $m$ and $n$ be positive integers.
Show that the complete bipartite graph $K_{m,n}$ has the same number of edges as its complement if and only if $m$ and $n$ are consecutive triangular numbers.\footnote{The definitions of the \href{https://en.wikipedia.org/wiki/Complete_bipartite_graph}{complete bipartite graph} and the \href{https://en.wikipedia.org/wiki/Complement_graph}{complement of a graph} can be found on Wikipedia.}


\item % Malwande?
Find all positive integers $n$ such that $\displaystyle \floor{\frac{n}{2}} \cdot \floor{\frac{n}{3}} \cdot \floor{\frac{n}{4}} = n^2$, where $\floor{x}$ denotes the greatest integer not greater than $x$.


\item % Iran
Let $\Gamma_1$ be a circle with a point $O$ on it.
Let $\Gamma_2$ be a circle centred at $O$ and let $P$ and $Q$ be the intersection points of $\Gamma_1$ and $\Gamma_2$.
Let $\Gamma_3$ be a circle which is externally tangent to $\Gamma_2$ at a point $R$ and internally tangent to $\Gamma_1$ at a point $S$.
Suppose that $Q$, $R$, and $S$ are collinear.
Let $A$ and $B$ be the other intersection points of $PR$ and $OR$ with $\Gamma_1$.
Prove that $QA$ is parallel to $SB$.


\item % Israel training problems 5771, 2018
Let $m$ and $n$ be positive integers such that $\displaystyle \frac{m}{n} < \sqrt{23}$.
Show that $\displaystyle \frac{m}{n} +\frac{3}{mn} < \sqrt{23}$.


\item % Malwande?
Find all functions $f : \mathbb{Q} \times \mathbb{Q} \to \mathbb{Q}$ such that for all $x, y, z \in \mathbb{Q}$ we have
\[ f(x,y) +f(y,z) +f(z,x) = f(0,x+y+z). \]


\item % Israel training problems 5772, 2018
There are $2023$ students in a school.
A group of students is called \emph{friendly} if each pair of students in it are friends.
There is at least one friendly group of $1012$ students at the school, but there is no friendly group of $1013$ students.
Prove that there is at least one student such that every friendly group of $1012$ students contains this student.


\item % Israel training problems 5773, 2018
Consider vectors $(m,n,p)$ in 3D space with integer coordinates.
We say that two vectors point in the same direction if each one is a multiple of the other, and we call a vector \emph{primitive} if it has the shortest length among vectors pointing in its direction.
Let $P$ be a primitive vector and consider the collection $\mathcal{D}$ of vectors with integer coordinates which are orthogonal to $P$.
Consider pairs of vectors in $\mathcal{D}$ which do not point in the same direction, and the parallelograms created by such pairs.
Prove that the smallest possible area of such a parallelogram is equal to the length of $P$.

\end{enumerate}


\vfill
\small
\begin{itemize}
	\item Submit your solutions at \href{https://forms.gle/9EBuvypU7ppDmprt8}{https://forms.gle/9EBuvypU7ppDmprt8}.
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\end{document}
