\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large March Intermediate Monthly Problem Set}
  \\ \vspace{1em}
  \textbf{\large Due: 31 March 2023}
\end{center}

\bigskip

\begin{enumerate}[itemsep=\fill]

\item %Latvia Prepatory Olympiad 91/92 Grade 6 Numbered 9

Can you enumerate a pentagon's edges and diagonals with natural numbers from 1 to 10 so that for every triangle having vertices which are vertices of the pentagon the sum of the numbers on its edges is the same?

\item %48th Belarussian Mathematical Olympiad 1998 Round 3 Category B Question 1

Prove that the number $(a_1^2+a_2^2 + \dots + a_{12}^2)a_1^2a_2^2 \dots a_{12}^2$ is divisible by 12 for all positive integers $a_1,a_2, \dots, a_{12}$.

\item %Latvia Problems of PLC 92/93 Seventh Tour

\begin{itemize}
%Group A Numbered 303
\item [(a)] Is it possible that the midpoints of four edges of a non-self-intersecting hexagon all belong to the same line?
%Group B Numbered 309
\item [(b)] Is it possible that the midpoints of five edges of a non-self-intersecting hexagon all belong to the same line?
\end{itemize}

\item %Latvia Problems of PLC 92/93 Seventh Tour Group B Numbered 310

Last summer 99 dwarfs used 99 houses, each one of them using a different house. This summer they have changed houses. Prove that each house can be coloured white, red or green so that each dwarf has used houses of different colours during these two summers.

\item %Latvia Problems of PLC 92/93 Seventh Tour Group B Numbered 313

Point $O$ is in the interior of an equilateral triangle $ABC$. Prove that there exists a triangle with edges equal to $OA$, $OB$ and $OC$.

\item %Latvia Problems of PLC 92/93 Fifth Tour Group B Numbered 286

Prove for each positive $a$, $b$, $c$ that $$1 < \frac{a}{a+b} + \frac{b}{b+c} + \frac{c}{c+a} < 2$$

\end{enumerate}


\vfill
\small
\begin{itemize}
	\item Submit your solutions at \href{https://forms.gle/9EBuvypU7ppDmprt8}{https://forms.gle/9EBuvypU7ppDmprt8}.
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}


\vfill
% ASCII art
\centering
\scriptsize
\begin{BVerbatim}
                 _.--"""-,
               .'         `\
              /   _         \
 .-""-.       |  (O\.--.-.-/O)          .-""-.
/ O O  \      .\|(_._.__._.__)         /  O O \
|O .-.  \    (   )   0 _ 0   \        /  .-. O|
\ (   )  '.   `-|     (_)     |     .'  (   ) /
 '.`-'     '-./`|             |`\.-'     '-'.'
   \         |  \   \     /   /  |         /
    \        \   '.  '._.'  .'   /        /
     \        '.   `'-----'`   .'        /
      \   .'    '-._        .-'\   '.   /
       |/`          `'''''')    )    `\|
       /                  (    (      ,\
      ;                    \    '-..-'/ ;
      |                     '.       /  |
      |                       `'---'`   |
      ;                                 ;
       \                               /
        `.                           .'
          '-._                   _.-'
           __/`"  '  - - -  ' "`` \__
         /`            /^\           `\
         \(          .'   '.         )/
          '.(__(__.-'       '.__)__).'
\end{BVerbatim}

\end{document}
