\documentclass{article}

\usepackage{mathtools,amsfonts}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{hyperref}


\begin{document}
\thispagestyle{empty}

\begin{center}
  \textbf{\Large January Intermediate Monthly Problem Set}
  \\ \vspace{1em}
  \textbf{\large Due: 13 January 2023}
\end{center}

\bigskip \bigskip

\begin{enumerate}[itemsep=\fill]

\item % Talent Search, 2006
Find the last two digits of 6^{2023}?
 
\item % Talent Search, 2006
What is the area of the triangle with side lengths 10, 17 and 21?


\item % Moldova Olympiad, 2014
Find the natural number $a$ for which $N = (a^{2} + 85)^{2} - (18a+3)^{2}$ is prime.


\item % RuMO 2015/16 G9 Q4
King Hiero has 11 metal pieces indistinguishable in appearance. The king knows that their weights in some order are $1,2,...,11$ kg. The king also has a bag that breaks if it contains more than 11 kg (it will not break if it contains exactly 11 kg). Archimedes knows the weight of each piece and he wants to convince King Hiero beyond a shadow of a doubt about which piece has the 1 kg weight. By a `move', Archimedes can put several pieces into the king bag to demonstrate that the bag is still not broken (He may not break the bag!). Find the least number of moves Archimedes needs to convince King Hiero. 


\item % Tournament of Towns, Spring 2015
Points $K$, and $L$ are marked on side $AB$ of triangle $ABC$ so that $KL=BC$ and $AK=LB$. Given that $O$ is the midpoint of side $AC$, prove that $\angle{KOL} = 90^{\circ}$


\item % RuMO 2015/16 G9 Q6
We say that a non-empty set $A$ consisting of positive integers is \textit{complete} if for any positive integers $a$ and $b$ such that $a+b\in A$, the number $ab$ also lies in $A$ (the numbers $a$ and $b$ are not required to be distinct or to belong to $A$). Find all complete sets.

\end{enumerate}


\vfill
\small
\begin{itemize}
	\item Submit your solutions at \href{https://forms.gle/9EBuvypU7ppDmprt8}{https://forms.gle/9EBuvypU7ppDmprt8}
	\item Submit each question in a single separate PDF file (with multiple pages if necessary).
	\item If you take photographs of your work, use a document scanner such as Office Lens to convert to PDF.
	\item If you have multiple PDF files for a question, combine them using software such as PDFsam.
\end{itemize}

\vfill
% ASCII art
\centering
\small
\begin{BVerbatim}
% INSERT ART HERE
\end{BVerbatim}

\end{document}
